---
title: "`r strftime(Sys.Date(), '%b %Y')`"
subtitle: 'Loss Forecasting MBR'
output: 
  powerpoint_presentation:
    reference_doc: template_16_9.pptx
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = F)

library(here)
library(data.table)
library(ggplot2)
library(flextable)

DAT_STEP = '01'
PRE_STEP = '02'
CUR_STEP = '03'

### Parameters for the whole presentation
CUR_CP = 6.8
DP = readRDS(here(DAT_STEP, 'date_params.rds'))

## ggplot theme
theme_set(theme_bw())
theme_update(text = element_text(size = 9), 
             axis.title = element_blank(),
             legend.position = 'bottom',
             plot.title = element_text(size = 11, hjust = 0.5))

### Parameters for each section

## Go forward section
Por_Plot_X_LB = as.Date('2021-02-28')
Por_Plot_X_UB = DP$Period_Actual_UB
PORT_LBS = readRDS(here(PRE_STEP, 'PORT_LBS.rds'))
QTRS = c('2021_Q4', '2022_Q1', '2022_Q2', '2022_Q3')
ASOFS = readRDS(here(PRE_STEP, 'ASOFS.rds'))

## Act vs Exp Plots (with delinquency implied forecast)
A_vs_E_X_LB = as.Date('2019-01-31')
# A_vs_E_X_UB = DP$Period_Implied_UB # use this for 3 months of DLQ implied on plot
# use this for 2 months of DLQ implied on plot
A_vs_E_X_UB = lubridate::floor_date(DP$Period_Implied_UB, 'month') - 1
A_vs_E_Lab_LB = as.Date('2021-07-31')

## Loss by MoB
YRS_QTRS = c('2018', '2019', '2020',
             '2021_Q1', '2021_Q2', '2021_Q3', '2021_Q4', 
             '2022_Q1', '2022_Q2', '2022_Q3', '2022_Q4')
Loss_X_UB = 48

## DLQ by MoB
DLQ_X_UB = 12

# Plotting functions
source(here(CUR_STEP, 'plot_fns.R'))
```




## Segment Originations and Actual-v-Model Performance
```{r}
df = readRDS(here(PRE_STEP, 'summary.rds'))
summary_table(df)
```




## Go-Forward Expectations -- Core T1-T3 -- CP `r CUR_CP`
```{r, fig.height=5, fig.width=10.6, dpi=320}
# Datasets for go forward section - overall
df_v = readRDS(here(PRE_STEP, 'C_Y_M.rds'))
df_p = readRDS(here(PRE_STEP, 'C_Y_A_por.rds'))
aDF = readRDS(here(PRE_STEP, 'aC_Y_A_por.rds'))

DF_V = df_v[orig_grp %in% QTRS]
DF_P = df_p[between(asofdate, Por_Plot_X_LB, Por_Plot_X_UB)]

forward_vin_por_plot(DF_V, DF_P, aDF)
```

## Go-Forward Expectations -- Tier 1 -- CP `r CUR_CP`
```{r, dpi=320, fig.width=10.6, fig.height=5}
# Datasets for go forward section - By Tier
df_v = readRDS(here(PRE_STEP, 'C_Y_M_tier.rds'))
df_p = readRDS(here(PRE_STEP, 'C_Y_A_por_tier.rds'))
aDF = readRDS(here(PRE_STEP, 'aC_Y_A_por_tier.rds'))

DF_V = df_v[orig_grp %in% QTRS]
DF_P = df_p[between(asofdate, Por_Plot_X_LB, Por_Plot_X_UB)]

TIER = 'Tier 1'
forward_vin_por_plot(DF_V[segment == TIER], DF_P[segment == TIER], aDF[segment == TIER])
```

## Go-Forward Expectations -- Tier 2 -- CP `r CUR_CP`
```{r, dpi=320, fig.width=10.6, fig.height=5}
TIER = 'Tier 2'
forward_vin_por_plot(DF_V[segment == TIER], DF_P[segment == TIER], aDF[segment == TIER])
```

## Go-Forward Expectations -- Tier 3 -- CP `r CUR_CP`
```{r, dpi=320, fig.width=10.6, fig.height=5}
TIER = 'Tier 3'
forward_vin_por_plot(DF_V[segment == TIER], DF_P[segment == TIER], aDF[segment == TIER])
```

## Risk Multiple by Tier -- CP `r CUR_CP`
```{r, dpi=320, fig.width=6, fig.height=5}
bDF = readRDS(here(PRE_STEP, 'bC_Y_A_por_tier.rds'))
mul_by_tier_plot(bDF)
```

## Go-Forward Expectations -- Term 24 -- CP `r CUR_CP`
```{r, dpi=320, fig.width=10.6, fig.height=5}
# Datasets for go forward section - By Term
df_v = readRDS(here(PRE_STEP, 'C_Y_M_term.rds'))
df_p = readRDS(here(PRE_STEP, 'C_Y_A_por_term.rds'))
aDF = readRDS(here(PRE_STEP, 'aC_Y_A_por_term.rds'))

DF_V = df_v[orig_grp %in% QTRS]
DF_P = df_p[between(asofdate, Por_Plot_X_LB, Por_Plot_X_UB)]

TERM = 24
forward_vin_por_plot(DF_V[term == TERM], DF_P[term == TERM], aDF[term == TERM])
```

## Go-Forward Expectations -- Term 36 -- CP `r CUR_CP`
```{r, dpi=320, fig.width=10.6, fig.height=5}
TERM = 36
forward_vin_por_plot(DF_V[term == TERM], DF_P[term == TERM], aDF[term == TERM])
```

## Go-Forward Expectations -- Term 48 -- CP `r CUR_CP`
```{r, dpi=320, fig.width=10.6, fig.height=5}
TERM = 48
forward_vin_por_plot(DF_V[term == TERM], DF_P[term == TERM], aDF[term == TERM])
```

## Go-Forward Expectations -- Term 60 -- CP `r CUR_CP`
```{r, dpi=320, fig.width=10.6, fig.height=5}
TERM = 60
forward_vin_por_plot(DF_V[term == TERM], DF_P[term == TERM], aDF[term == TERM])
```





## Section 1: Core, Applying Current Policy

## Core T1-T3 -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'C_Y_A.rds'))

DF = df[between(asofdate, A_vs_E_X_LB, A_vs_E_X_UB)]
act_vs_exp_w_dlq_plot(DF)
```

## Tier 1 -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset - By Tier
df = readRDS(here(PRE_STEP, 'C_Y_A_tier.rds'))

DF = df[between(asofdate, A_vs_E_X_LB, A_vs_E_X_UB)]

TIER = 'Tier 1'
act_vs_exp_w_dlq_plot(DF[segment == TIER])
```

## Tier 2 -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
TIER = 'Tier 2'
act_vs_exp_w_dlq_plot(DF[segment == TIER])
```

## Tier 3 -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
TIER = 'Tier 3'
act_vs_exp_w_dlq_plot(DF[segment == TIER])
```

## $ Loss Rate by MoB vs Exp (`r DP$Expectation_Range`) -- CP `r CUR_CP`
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'C_Y_M.rds'))
cum_loss_rates_plot(df[orig_grp %in% c('Expectation', YRS_QTRS) & monthonbook <= Loss_X_UB])
```

## $ DQ 31+ Rate by MoB -- CP `r CUR_CP`
```{r, dpi=320, fig.width=8, fig.height=5}
dlq_30_rates_plot(df[orig_grp %in% YRS_QTRS & monthonbook <= DLQ_X_UB]) +
  scale_x_continuous(breaks = seq(0, DLQ_X_UB, by = 2))
```




## Section 2: Core, Without Current Policy

## Core T1-T5 -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'C_N_A.rds'))

DF = df[between(asofdate, A_vs_E_X_LB, A_vs_E_X_UB)]
act_vs_exp_w_dlq_plot(DF)
```

## Tier 1 -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset - By Tier
df = readRDS(here(PRE_STEP, 'C_N_A_tier.rds'))

DF = df[between(asofdate, A_vs_E_X_LB, A_vs_E_X_UB)]

TIER = 'Tier 1'
act_vs_exp_w_dlq_plot(DF[segment == TIER])
```

## Tier 2 -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
TIER = 'Tier 2'
act_vs_exp_w_dlq_plot(DF[segment == TIER])
```

## Tier 3 -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
TIER = 'Tier 3'
act_vs_exp_w_dlq_plot(DF[segment == TIER])
```

## Tier 4 -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
TIER = 'Tier 4'
act_vs_exp_w_dlq_plot(DF[segment == TIER])
```

## Tier 5 -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
TIER = 'Tier 5'
act_vs_exp_w_dlq_plot(DF[segment == TIER])
```

## $ Loss Rate by MoB vs Exp (`r DP$Expectation_Range`) -- CP `r CUR_CP`
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'C_N_M.rds'))
cum_loss_rates_plot(df[orig_grp %in% c('Expectation', YRS_QTRS) & monthonbook <= Loss_X_UB])
```

## $ DQ 31+ Rate by MoB -- CP `r CUR_CP`
```{r, dpi=320, fig.width=8, fig.height=5}
dlq_30_rates_plot(df[orig_grp %in% YRS_QTRS & monthonbook <= DLQ_X_UB]) +
  scale_x_continuous(breaks = seq(0, DLQ_X_UB, by = 2))
```




## Section 3: Total Portfolio, Applying Current Policy

## Total Portfolio -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'T_Y_A.rds'))

DF = df[between(asofdate, A_vs_E_X_LB, A_vs_E_X_UB)]
act_vs_exp_w_dlq_plot(DF)
```

## $ Loss Rate by MoB vs Exp (`r DP$Expectation_Range`) -- CP `r CUR_CP`
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'T_Y_M.rds'))
cum_loss_rates_plot(df[orig_grp %in% c('Expectation', YRS_QTRS) & monthonbook <= Loss_X_UB])
```

## $ DQ 31+ Rate by MoB -- CP `r CUR_CP`
```{r, dpi=320, fig.width=8, fig.height=5}
dlq_30_rates_plot(df[orig_grp %in% YRS_QTRS & monthonbook <= DLQ_X_UB]) +
  scale_x_continuous(breaks = seq(0, DLQ_X_UB, by = 2))
```




## Section 4: Total Portfolio, Without Current Policy

## Total Portfolio -- CP `r CUR_CP` -- Actual vs Expected Charge Off
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'T_N_A.rds'))

DF = df[between(asofdate, A_vs_E_X_LB, A_vs_E_X_UB)]
act_vs_exp_w_dlq_plot(DF)
```

## $ Loss Rate by MoB vs Exp (`r DP$Expectation_Range`) -- CP `r CUR_CP`
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'T_N_M.rds'))
cum_loss_rates_plot(df[orig_grp %in% c('Expectation', YRS_QTRS) & monthonbook <= Loss_X_UB])
```

## $ DQ 31+ Rate by MoB -- CP `r CUR_CP`
```{r, dpi=320, fig.width=8, fig.height=5}
dlq_30_rates_plot(df[orig_grp %in% YRS_QTRS & monthonbook <= DLQ_X_UB]) +
  scale_x_continuous(breaks = seq(0, DLQ_X_UB, by = 2))
```




## Section 5: Monitoring Populations Removed by Recent CPs

## CP 6.5-6.6
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'CP65_N_A.rds'))

DF = df[between(asofdate, A_vs_E_X_LB, A_vs_E_X_UB)]
act_vs_exp_w_dlq_plot(DF)
```

## CP 6.7
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'CP67_N_A.rds'))

DF = df[between(asofdate, A_vs_E_X_LB, A_vs_E_X_UB)]
act_vs_exp_w_dlq_plot(DF)
```

## CP 6.8
```{r, dpi=320, fig.width=8, fig.height=5}
# Dataset
df = readRDS(here(PRE_STEP, 'CP68_N_A.rds'))

DF = df[between(asofdate, A_vs_E_X_LB, A_vs_E_X_UB)]
act_vs_exp_w_dlq_plot(DF)
```